title: "Dual Luciferase Assay"
output: 
  html_document: 
    highlight: tango
    keep_md: yes
    number_sections: yes
    toc: yes
---

# Aim

The Aim of this file is to load luciferase-based assay data containing a Firefly (FLUC) as well as an Renilla (RLUC) luciferase signal.  
RLUC is considered as the normalization signal, e.g. cell number, whereas FLUC contains the phenotype signal.

# Load Data

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Path yo XLS and assay files
path <- "/Users/janwinter/OneDrive/PhD/Followup/Results/Luciferase/Assays/2017-03-21_Round1_1/2017-03-21_HEK-HCT_Round1_1.xlsx"
# Name of XLS sheet
excel.sheet <- file.path(path,"2017-03-21_HEK-HCT_Round1_1.xlsx")

# Name of Assay files
## Must be named like:
## NAME_PlateX-RLUC/FLUC
# Will be automatically read according to the entry in the XLS sheet

name <- "20161205_Hek293-HCT116"

# Median normalization?
normalize = FALSE
```


## Load XLS Overview file

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(openxlsx)
library(reshape2)
library(dplyr)
library(highcharter)

# Get XLS File

knitr::opts_chunk$set(root.dir = path)



# Open XLSX File
## File is structured in the following way
## Worksheets:  Protocol (contains Aim, FLUC, RLUC, Treatment)
##              Sheet1 (Sheet2 etc.) containing the 96 well plate as plate format, 1-12 in rows A-H, which needs to be pared into a data frame

workbook <- openxlsx::loadWorkbook(excel.sheet,xlsxFile = NULL)
wb_names <- names(workbook)


# Get Protocol
protocols <- openxlsx::read.xlsx(xlsxFile = excel.sheet, sheet = "Protocol", colNames = FALSE, rowNames = FALSE)
protocol <- protocols[,2]
names(protocol) <- protocols[,1]

# Get Sheets
plates <- list()
groups <- NA
## check if multiple
for(i in 2:length(wb_names))
{
  if(grepl(pattern = "Plate.+", x=wb_names[i]) )
  {
    plates[[wb_names[i]]]$layout <- as.data.frame(openxlsx::read.xlsx(xlsxFile = excel.sheet, sheet = wb_names[i], colNames = TRUE, rowNames = TRUE), stringsAsFactors=FALSE)
    
    plates[[wb_names[i]]]$shape <- reshape2::melt(as.matrix(plates[[wb_names[i]]]$layout))
    pattern <- expression("^(\\d{1})$")
    plates[[wb_names[i]]]$shape$Var2 <- sub(pattern = pattern, replacement = paste("0","\\1", sep=""), x=  plates[[wb_names[i]]]$shape$Var2, fixed = FALSE )
    plates[[wb_names[i]]]$shape$position <- paste0(plates[[wb_names[i]]]$shape$Var1, plates[[wb_names[i]]]$shape$Var2)
    
    # set treatment groups
    groups <- c(groups, as.character(plates[[wb_names[i]]]$shape$value))
    
  }
  
}

# Now we make treatment groups in list
## They will be used for plotting later, NA are wells that will not be used for anything later on
groups <- unique(groups) # might be used later

# according to tidyverse, data will be kept like that:
## Column1: treatment
## Column2: FLUC signal
## Column3: RLUC signal


# We achieve this by loading the data, parsing the position as plate X at well A12 and putting it together with the treatment in the row.
# this rrequires that FLUC and RLUC signals of the same plate are in the same dataframe
```


## Load TXT Files with Sample Data

Two files, one for each Luciferase Signal

```{r, echo=FALSE, warning=FALSE, message=FALSE}
data <- as.list(names(plates))
names(data) <- names(plates)

library(readr)

for(i in 1:length(data))
{
  # FLUC
  data[[i]]$FLUC <- readr::read_tsv(file = file.path(path,paste(name,"_",names(data)[i],"-FLUC.TXT", sep="")), col_names=FALSE, quoted_na = FALSE)
  colnames(data[[i]]$FLUC) <- c("Plate", "Well", "FLUC")
  data[[i]]$FLUC$Plate <- NULL
  # RLUC
  data[[i]]$RLUC <- readr::read_tsv(file = file.path(path,paste(name,"_",names(data)[i],"-RLUC.TXT", sep="")), col_names=FALSE, quoted_na = FALSE)
  colnames(data[[i]]$RLUC) <- c("Plate", "Well", "RLUC")
  data[[i]]$RLUC$Plate <- NULL
  
  # Combine them in one
  data[[i]]$ALL <- dplyr::inner_join(data[[i]]$FLUC, data[[i]]$RLUC, by="Well")
  data[[i]]$ALL$Plate <- paste("Plate",i,sep="")
  
  # Median normaliziation
  if(normalize){
    data[[i]]$ALL$FLUC <- data[[i]]$ALL$FLUC/ median(data[[i]]$ALL$FLUC, na.rm = TRUE)
    data[[i]]$ALL$RLUC <- data[[i]]$ALL$RLUC/ median(data[[i]]$ALL$RLUC, na.rm = TRUE)
  }
  
  # Add the treatment to it
  data[[i]]$ALL$Treatment <- sapply(data[[i]]$ALL$Well, function(x){
    # Get treatment for same plate from plates$Plate1$[plates$Plate1$$position == x , "value"]
     return(as.character(plates[[names(data)[i]]]$shape[plates[[names(data)[i]]]$shape$position == as.character(x),"value"]))
  })
  
  # Remove NA
  data[[i]]$ALL <- dplyr::filter(data[[i]]$ALL, !is.na(Treatment))
  
  # Create Platemap
  data[[i]]$platemap <- dplyr::mutate(as.data.frame(data[[i]]$ALL),
                   Row=as.numeric(match(toupper(substr(Well, 1, 1)), LETTERS)),
                   Column=as.numeric(substr(Well, 2, 5)))

}


```


```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Now we have all data in
# data$PLATEX#ALL in a row-based tidyverse compatible system

## Aim: Merge all to have a single tbl

plot <- list()

# store in plot$data
for(i in 1:length(data))
{
  if(i==1)
  {
    # create tbl
    plot$data <- tibble::tibble("Plate" = data[[i]]$ALL$Plate,
                                "Treatment" = data[[i]]$ALL$Treatment,
                                "FLUC" = data[[i]]$ALL$FLUC,
                                "RLUC" = data[[i]]$ALL$RLUC,
                                "Well" = data[[i]]$ALL$Well,
                                "FLUC.median" = NA,
                                    "FLUC.mean" = NA,
                                    "FLUC.sd" = NA,
                                    "RLUC.median" = NA,
                                    "RLUC.mean" = NA,
                                    "RLUC.sd" = NA
                                )
   
  }
  else{
    # Add rows of other datasets
    plot$data <- dplyr::bind_rows(plot$data, data[[i]]$ALL[,c("Plate", "Treatment", "FLUC", "RLUC", "Well")])
  }
}


## Normalize: FLUC / RLUC
plot$data$Divided <- plot$data$FLUC/plot$data$RLUC


## Transform to log2
plot$data$Log2 <- log2(plot$data$Divided)

# Transform Inf and -Inf to NA
plot$data$Divided <- sapply(plot$data$Divided, function(x){
  if(is.infinite(x) || is.nan(x)){
    return(NA)
  } else {
    return(x)
  }
})

plot$data$Log2 <- sapply(plot$data$Log2, function(x){
  if(is.infinite(x) || is.nan(x)){
    return(NA)
  } else {
    return(x)
  }
})
  
  

## Normalize
normalize=TRUE
if(normalize)
{
  
  # get samples available on all plates
  plates <- unique(plot$data$Plate)
  treatments <- unique(plot$data$Treatment)
  treatsall <- NULL
  for(i in 1:length(plates))
  {
    treatplate <- dplyr::filter(plot$data, Plate == plates[i]) %>% dplyr::filter(Treatment %in% treatments) %>% dplyr::select(Treatment)
    treatsall <- c(treatsall,treatplate$Treatment)
  }
  
  # check for samples that are at least x times (for x plates) in the vector
  output <- NULL
  for(i in 1:length(treatments))
  {
    if (sum(treatsall == treatments[i]) >= length(plates) )
    {
      output <- c(output, treatments[i])
    }
  }
  
  
  method <- "Plate Median"
  
  
  
}
  
  
```

# Data Overview

## Samples

```{r sample-overview, fig.width=10, fig.height=7, resuls='asis', dpi=300, echo=FALSE, warning=FALSE, message=FALSE}
library(ggplot2)
cat("\n")
for(i in 1:length(data))
{
  
  cat("\n")
  cat("### ", names(data)[i])
  cat("\n")
  # PLate Overview of Samples
  platemap <- dplyr::mutate(plates[[names(data)[i]]]$shape,
                   Row=as.numeric(match(toupper(substr(position, 1, 1)), LETTERS)),
                   Column=as.numeric(substr(position, 2, 5)))
  
  g <- ggplot2::ggplot(data=platemap, aes(x=Column, y=Row)) +
    geom_point(data=expand.grid(seq(1, 12), seq(1, 8)), aes(x=Var1, y=Var2),
               color="grey90", fill="white", shape=21, size=6) +
    geom_point(aes(color=value), size=6) +
    coord_fixed(ratio=(13/12)/(9/8), xlim=c(0.5, 12.5), ylim=c(0.5, 8.5)) +
    scale_y_reverse(breaks=seq(1, 8), labels=LETTERS[1:8]) +
    scale_x_continuous(breaks=seq(1, 12)) +
  scale_shape_manual(values=seq(from=0, to = length(unique(platemap$value)), by=1 ) ) +
    labs(title="Plate Layout: Sample Types") 
  
  
 
  
  print(g)
}


```

## Data


```{r data-overview, results='asis', dpi=300, echo=FALSE, warning=FALSE, message=FALSE}

cat("\n")
for(i in 1:length(data))
{
  cat("\n")
  data_use <- dplyr::filter(plot$data, Plate == names(data)[i])
  # if no treatment is specified -> set to NA
  data_use[is.na(data_use$Treatment),c("Treatment","FLUC","RLUC","Divided","Log2")] <- NA
  
  cat("\n")
  cat("### ", names(data)[i])
  cat("\n")
  
  # Plate Overview of Samples
  platemap <- dplyr::mutate(data_use,
                   Row=as.numeric(match(toupper(substr(Well, 1, 1)), LETTERS)),
                   Column=as.numeric(substr(Well, 2, 5)))
  cat("\n")
  cat("### ", "TCF Reporter FLUC")
  cat("\n")
  # FLUC
  
  g <- ggplot2::ggplot(data=platemap, aes(x=Column, y=Row)) +
    geom_point(data=expand.grid(seq(1, 12), seq(1, 8)), aes(x=Var1, y=Var2),
               color="grey90", fill="white", shape=21, size=6) +
    geom_point(aes(color=FLUC), size=6) +
    coord_fixed(ratio=(13/12)/(9/8), xlim=c(0.5, 12.5), ylim=c(0.5, 8.5)) +
    scale_y_reverse(breaks=seq(1, 8), labels=LETTERS[1:8]) +
    scale_x_continuous(breaks=seq(1, 12)) +
  #scale_shape_manual(values=seq(from=0, to = length(unique(platemap$value)), by=1 ) ) +
    labs(title=paste("Plate Layout:", "FLUC", names(data)[i], sep=" ") )
  
  print(g)
  
  
  # RLUC
  cat("\n")
  cat("### ", "TCF Reporter FLUC")
  cat("\n")
  
  g <- ggplot2::ggplot(data=platemap, aes(x=Column, y=Row)) +
    geom_point(data=expand.grid(seq(1, 12), seq(1, 8)), aes(x=Var1, y=Var2),
               color="grey90", fill="white", shape=21, size=6) +
    geom_point(aes(color=RLUC), size=6) +
    coord_fixed(ratio=(13/12)/(9/8), xlim=c(0.5, 12.5), ylim=c(0.5, 8.5)) +
    scale_y_reverse(breaks=seq(1, 8), labels=LETTERS[1:8]) +
    scale_x_continuous(breaks=seq(1, 12)) +
  #scale_shape_manual(values=seq(from=0, to = length(unique(platemap$value)), by=1 ) ) +
    labs(title=paste("Plate Layout:", "RLUC", names(data)[i], sep=" ") )
  
  print(g)
  
  
  #  Divided
  cat("\n")
  cat("### ", "TCF Reporter FLUC normalized to RLUC")
  cat("\n")
  
  g <- ggplot2::ggplot(data=platemap, aes(x=Column, y=Row)) +
    geom_point(data=expand.grid(seq(1, 12), seq(1, 8)), aes(x=Var1, y=Var2),
               color="grey90", fill="white", shape=21, size=6) +
    geom_point(aes(color=Divided), size=6) +
    coord_fixed(ratio=(13/12)/(9/8), xlim=c(0.5, 12.5), ylim=c(0.5, 8.5)) +
    scale_y_reverse(breaks=seq(1, 8), labels=LETTERS[1:8]) +
    scale_x_continuous(breaks=seq(1, 12)) +
  #scale_shape_manual(values=seq(from=0, to = length(unique(platemap$value)), by=1 ) ) +
    labs(title=paste("Plate Layout:", "Normalized Activity", names(data)[i], sep=" ") )
  
  print(g)
  
  
}

```



# Results

## Treatment Group Statistics

```{r treatmentstatistics, results='asis', echo=FALSE, warning=FALSE, message=FALSE}
# Data is stored in plot$data
# compare groups

treatmentgroups <- tibble::tibble("Treatment" = groups,
                         "FLUC.median" = NA,
                         "FLUC.mean" = NA,
                         "FLUC.sd" = NA,
                         "RLUC.median" = NA,
                         "RLUC.mean" = NA,
                         "RLUC.sd" = NA
                         )
treatmentgroups <- treatmentgroups[-is.na(treatmentgroups$Treatment),]

treatmentgroups$FLUC.mean <- sapply(treatmentgroups$Treatment, function(x){
    return(mean(plot$data[plot$data$Treatment == as.character(x),"FLUC"]$FLUC, na.rm=TRUE))
})
treatmentgroups$FLUC.median <- sapply(treatmentgroups$Treatment, function(x){
    return(median(plot$data[plot$data$Treatment == as.character(x),"FLUC"]$FLUC, na.rm=TRUE))
})
treatmentgroups$FLUC.sd <- sapply(treatmentgroups$Treatment, function(x){
    return(sd(plot$data[plot$data$Treatment == as.character(x),"FLUC"]$FLUC, na.rm=TRUE))
})

treatmentgroups$RLUC.mean <- sapply(treatmentgroups$Treatment, function(x){
    return(mean(plot$data[plot$data$Treatment == as.character(x),"RLUC"]$RLUC, na.rm=TRUE))
})
treatmentgroups$RLUC.median <- sapply(treatmentgroups$Treatment, function(x){
    return(median(plot$data[plot$data$Treatment == as.character(x),"RLUC"]$RLUC, na.rm=TRUE))
})
treatmentgroups$RLUC.sd <- sapply(treatmentgroups$Treatment, function(x){
    return(sd(plot$data[plot$data$Treatment == as.character(x),"RLUC"]$RLUC, na.rm=TRUE))
})

treatmentgroups$activity.mean <- treatmentgroups$FLUC.mean / treatmentgroups$RLUC.mean
#dplyr::arrange(treatmentgroups, Treatment)

# add SD to plot$data so that it can be used for more plot
for(i in 1:nrow(plot$data)) {
  
  plot$data$FLUC.median[i] <- treatmentgroups$FLUC.median[treatmentgroups$Treatment == plot$data$Treatment[i]]
  plot$data$FLUC.mean[i] <- treatmentgroups$FLUC.mean[treatmentgroups$Treatment == plot$data$Treatment[i]]
  plot$data$FLUC.sd[i] <- treatmentgroups$FLUC.sd[treatmentgroups$Treatment == plot$data$Treatment[i]]
  plot$data$RLUC.median[i] <- treatmentgroups$RLUC.median[treatmentgroups$Treatment == plot$data$Treatment[i]]
  plot$data$RLUC.mean[i] <- treatmentgroups$RLUC.mean[treatmentgroups$Treatment == plot$data$Treatment[i]]
  plot$data$RLUC.sd[i] <- treatmentgroups$RLUC.sd[treatmentgroups$Treatment == plot$data$Treatment[i]]
}

DT::datatable(treatmentgroups)
```



## Plots

```{r plots, results='asis', dpi=300, echo=FALSE, warning=FALSE, message=FALSE}
# Boxplots with rawdata activity, no fold changes between groups
## in plot$data
##  Plate Treatment  FLUC  RLUC  Well Divided      Log2

# non-log transformed
  cat("\n")
  cat("### ", "Ratio")
  cat("\n")

p <- ggplot(plot$data, aes(x=Treatment, y=Divided, fill=Treatment)) + 
  geom_boxplot() +
  geom_jitter(shape=16, position=position_jitter(0.2)) +
  labs(title = "Ratio between FLUC and RLUC", x = "Samples", y = "FLUC / RLUC") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = rel(1.1)))
print(p)


# log2 transformed
  cat("\n")
  cat("### ", "Log2")
  cat("\n")
p <- ggplot(plot$data, aes(x=Treatment, y=Log2, fill=Treatment)) + 
  geom_boxplot() +
  geom_jitter(shape=16, position=position_jitter(0.2)) +
  labs(title = "Log2 Ratio between FLUC and RLUC", x = "Samples", y = "FLUC / RLUC") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = rel(1.1)))
print(p)



# RLUC
  cat("\n")
  cat("### ", "RLUC")
  cat("\n")
p <- ggplot(plot$data, aes(x=Treatment, y=RLUC, fill=Treatment)) + 
  geom_boxplot() +
  geom_jitter(shape=16, position=position_jitter(0.2)) +
  labs(title = "RLUC", x = "Samples", y = "RLUC") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = rel(1.1)))
print(p)

# FLUC
  cat("\n")
  cat("### ", "FLUC")
  cat("\n")
p <- ggplot(plot$data, aes(x=Treatment, y=FLUC, fill=Treatment)) + 
  geom_boxplot() +
  geom_jitter(shape=16, position=position_jitter(0.2)) +
  labs(title = "FLUC", x = "Samples", y = "FLUC") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = rel(1.1)))
print(p)



```





# Special Plots

```{r specialplots, results='asis', dpi=300, echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}
# Here only manually curated plots come into place
library(ggplot2)
library(highcharter)

# Compare NON-Transduced
datas <- list()
datas[1] <- list(dplyr::filter(plot$data, Treatment %in% c("APC","CSNK1A1",	"Topflash",	"CFC1",	"GDE1","B4GALT6","TTLL4","PLGRKT","IDO1","px459_p1")))
datas[2] <- list(dplyr::filter(plot$data, Treatment %in% c("Topflash", "CFC1",	"GDE1","B4GALT6","TTLL4","PLGRKT","IDO1","px459_p1","RLUC")))
datas[3] <- list(dplyr::filter(plot$data, Treatment %in% c("APC",	"APC_50",	"CSNK1A1",	"CSNK1A1_50", "Topflash", "Topflash_50","RLUC_50")))
datas[4] <- list(dplyr::filter(plot$data, Treatment %in% c("Topflash_50", "CFC1_50",	"GDE1_50","B4GALT6_50","TTLL4_50","PLGRKT_50","IDO1_50","px459_p1_50")))
datas[5] <- list(dplyr::filter(plot$data, Treatment %in% c("Topflash","Topflash_50","CFC1", "CFC1_50","GDE1", "GDE1_50","B4GALT6","B4GALT6_50","TTLL4","TTLL4_50","PLGRKT","PLGRKT_50","IDO1","IDO1_50","px459_p1","px459_p1_50") ))
datas[6] <- list(dplyr::filter(plot$data, Treatment %in% c("px459_p1", "px459_p1_50","px459_p2", "px459_p2_50", "px459_p3", "px459_p3_50", "px459_p4", "px459_p4_50")))
#datas[7] <- list(dplyr::filter(plot$data, Treatment %in% c("TransIT", "TransIT_100","APC1", "APC1_100",	"APC2", "APC2_100",	"BcatAxin1", "BcatAxin1_100")))

for(i in 1:length(datas))
{
  cat("\n")
  cat("### ", "Individual Comparisons")
  cat("\n")

p <- ggplot(datas[[i]], aes(x=Treatment, y=Divided, fill=Treatment)) + 
  geom_boxplot() +
  geom_jitter(shape=16, position=position_jitter(0.2)) +
  labs(title = "Ratio between FLUC and RLUC", x = "Samples", y = "FLUC / RLUC") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = rel(1.1)))
print(p)

p <- ggplot(datas[[i]], aes(x=Treatment, y=RLUC, fill=Treatment)) + 
  geom_boxplot() +
  geom_jitter(shape=16, position=position_jitter(0.2)) +
  labs(title = "RLUC", x = "Samples", y = "RLUC") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = rel(1.1)))
print(p)

p <- ggplot(datas[[i]], aes(x=Treatment, y=FLUC, fill=Treatment)) + 
  geom_boxplot() +
  geom_jitter(shape=16, position=position_jitter(0.2)) +
  labs(title = "FLUC", x = "Samples", y = "FLUC") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = rel(1.1)))
print(p)

#  cat("\n")
#   cat("### ", "Log2")
#   cat("\n")
# 
# p <- ggplot(datas[[i]], aes(x=Treatment, y=Log2, fill=Treatment)) + 
#   geom_boxplot() +
#   geom_jitter(shape=16, position=position_jitter(0.2)) +
#   labs(title = "Log2 Ratio between FLUC and RLUC", x = "Samples", y = "FLUC / RLUC") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = rel(1.1)))
# print(p)
#   

}



#### Make Foldchanges between samples

# between transIT and 0
compare = list( "APC 50 ng/mL vs APC" = c("APC_50", "APC"),
                "APC vs Control" = c("APC", "px459_p1"),
                "Topflash vs Control" = c("Topflash", "px459_p1"),
                "CSNK1A1 vs Control" = c("CSNK1A1","px459_p1"),
                "B4GALT6 vs Control" = c("B4GALT6", "px459_p1"),
                "B4GALT6 Wnt vs Control Wnt" = c("B4GALT6_50", "px459_p1_50"),
                "CFC1 vs Control" = c("CFC1", "px459_p1"),
                "CFC1 Wnt vs Control Wnt" = c("CFC1_50", "px459_p1_50"),
                "GDE1 vs Control" = c("GDE1", "px459_p1"),
                "GDE1 Wnt vs Control Wnt" = c("GDE1_50", "px459_p1_50"),
                "PLGRKT vs Control" = c("PLGRKT", "px459_p1"),
                "PLGRKT Wnt vs Control Wnt" = c("PLGRKT_50", "px459_p1_50"),
                "IDO1 vs Control" = c("IDO1", "px459_p1"),
                "IDO1 Wnt vs Control Wnt" = c("IDO1_50", "px459_p1_50"),
                "TTLL4 vs Control" = c("TTLL4", "px459_p1"),
                "TTLL4 Wnt vs Control Wnt" = c("TTLL4_50", "px459_p1_50")
                
                
                )

comparedata <- list()

for(i in 1:length(compare))
{
   comparedata[i] <- list( 
    data.frame("Name" = i,
               stringsAsFactors = FALSE)
  )
   data1 <- dplyr::filter(plot$data, Treatment %in% c(compare[[i]][1]))$Divided
   data2 <- dplyr::filter(plot$data, Treatment %in% c(compare[[i]][2]))$Divided
   comparedata[[i]]$median = median(data1) / median(data2)
   
   comparedata[[i]]$low <- (median(data1) - sd(data1, na.rm = TRUE)) / (median(data2) + sd(data2, na.rm = TRUE))
   comparedata[[i]]$high <- (median(data1) + sd(data1, na.rm = TRUE)) / (median(data2) - sd(data2, na.rm = TRUE))
     #median(comparedata[[i]]$median) + sd(comparedata[[i]]$median, na.rm = TRUE)
   
   
   #comparedata[[i]]$median <- median(comparedata[[i]]$median)
   #comparedata[[i]] <- unique(comparedata[[i]])

}  

names(comparedata) <- names(compare)

    hc2 <- highcharter::highchart() %>%
    highcharter::hc_chart(zoomType = "xy") %>%
    highcharter::hc_chart(type = "column") %>% 
    highcharter::hc_title(text = "Foldchange") %>%
    #highcharter::hc_subtitle(text = paste("between ", paste(compare[[i]], collapse = " and "))) %>%
    #highcharter::hc_xAxis(categories = list(unlist(names(comparedata)) ) ) %>%
    highcharter::hc_yAxis(title = list(text = "Median Foldchange")) %>%
    highcharter::hc_legend(enabled = TRUE) %>%
    highcharter::hc_exporting(enabled=TRUE)
    for(i in 1:length(comparedata))
    {
      hc2 <- highcharter::hc_add_series(hc2, name = names(comparedata)[i], data = comparedata[[i]]$median)
    }
    
    
    hc3 <- highcharter::highchart() %>% 
    highcharter::hc_title(text = "Median Foldchange") %>%
    highcharter::hc_subtitle(text = "with minimum and maximum calculations") %>%
    highcharter::hc_xAxis(categories = c("",names(comparedata))) %>%
    highcharter::hc_yAxis(title = list(text = "Median Foldchange +- min/max")) %>%
    highcharter::hc_legend(enabled = FALSE) %>%
    highcharter::hc_chart(zoomType = "xy") %>%
    highcharter::hc_exporting(enabled=TRUE)
    
    for(i in 1:length(comparedata))
    {
      colnames(comparedata[[i]]) <- c("x","y", "low", "high")
      hc3 <- highcharter::hc_add_series(hc3, data = comparedata[[i]],
                type = "errorbar", color = "grey", stemWidth = 3,  whiskerLength = 20, name = names(comparedata)[i])
      hc3 <- highcharter::hc_add_series(hc3, data = comparedata[[i]][,c("x","y")], color = "black", marker = list(radius = 5, symbol = "square"), name = names(comparedata)[i])
    }
    
    
      hc3
hc2



```































