---
title: "Incucyte Data Analysis"
output:
  html_document: default
  html_notebook: default
---

# Incucyte Data

This notebook provides infomration about Data derived from the Incucyte automated microscopy device.

## Data structure

Incucyte data must be structured the following way:  

`
Label: HEK_F_1
Metric: PhaseIM Confluence (Percent)
Cell Type: HEK293T_TCF
Passage: 1
Notes: 
Analysis Job: 2017-03-03_HEKTCF_sgRNA_viability1

Date Time	Elapsed	HEK_F_1: HEK293T_TCF (1) 50K / well
03.03.2017 20:00:00	0	5,722833
`

Each well is one column with the SAMPLE separated by the Plate name with a *:*.  
Replicates need to be set!  
If STDErr is also present, this will be always the column next to it!

## Setup parameters

```{r setup}
stderr_present <- FALSE
filepath <- "/Users/janwinter/OneDrive/PhD/Followup/Results/Microscopy/2017-03-03_24-well_sgRNATEST/"
filename <- "2017-03-06_replicates.txt"

```

STDErr is presnet in the file? `r stderr_present`  
File is located in `r filepath` with the name `r filename`.

## Data Handling

```{r load}

data <- readr:: read_tsv(file = file.path(filepath,filename),col_names = TRUE, skip = 7, locale = readr::locale(decimal_mark = ","))

# get correct colnames
col_names <- colnames(data)
## get all after the ","
col_names <- sub(pattern = "^.*,\\s+(.*)$", perl = TRUE, replacement = "\\1", x = col_names)

colnames(data) <- col_names
samples <- as.list(col_names[3:length(col_names)])
names(samples) <- col_names[3:length(col_names)]

data.raw <- data
```

## Raw Data

```{r datatable}

DT::datatable(data,class="stripe hover")

# Normalize Data with the FIRST value for each sample! -> column wise!
for(i in 3: length(col_names))
{
  # divide by the first element of the column
  data[[i]] <- data[[i]] / data[[i]][1]
}

DT::datatable(data,class="stripe hover")

```


# Plots

## Overall Plot

```{r plot-all-rawdata}
library(highcharter)

hc <- highcharter::highchart() %>%
  highcharter::hc_chart(type="spline",zoomType="xy")%>%
  highcharter::hc_title(text = "Cell Confluence") %>%
  highcharter::hc_subtitle(text = "for all sampled with median replicates") %>%
  highcharter::hc_xAxis(title = list(text = "Sample")) %>%
  highcharter::hc_yAxis(title = list(text = "Confluence in %")) %>%
  highcharter::hc_legend(enabled = TRUE) %>%
  highcharter::hc_exporting(enabled = TRUE,
                 printMaxWidth = 2000,
                 filename = paste(filename, "_Plot_all"),
                 scale=8,
                 formAttributes = list(target = "_blank")
                 )

  for(i in 1:length(samples))
  {
    plotdata <- data.raw[,c("Elapsed",names(samples)[i])]
    colnames(plotdata) <- c("x", "y")
    hc <- highcharter::hc_add_series(hc, data = plotdata, name = names(samples)[i])
  }

  hc <- highcharter::hc_tooltip(hc, crosshairs = TRUE, borderWidth = 0, delayForDisplay = 1500) %>%
    highcharter::hc_add_theme(highcharter::hc_theme_google())

hc


```

```{r plot-all}
library(highcharter)

hc <- highcharter::highchart() %>%
  highcharter::hc_chart(type="spline",zoomType="xy")%>%
  highcharter::hc_title(text = "Cell Confluence") %>%
  highcharter::hc_subtitle(text = "for all sampled with median replicates") %>%
  highcharter::hc_xAxis(title = list(text = "Sample")) %>%
  highcharter::hc_yAxis(title = list(text = "Normalized Confluence in Foldchange from Start")) %>%
  highcharter::hc_legend(enabled = TRUE) %>%
  highcharter::hc_exporting(enabled = TRUE,
                 printMaxWidth = 2000,
                 filename = paste(filename, "_Plot_all"),
                 scale=8,
                 formAttributes = list(target = "_blank")
                 )

  for(i in 1:length(samples))
  {
    plotdata <- data[,c("Elapsed",names(samples)[i])]
    colnames(plotdata) <- c("x", "y")
    hc <- highcharter::hc_add_series(hc, data = plotdata, name = names(samples)[i])
  }

  hc <- highcharter::hc_tooltip(hc, crosshairs = TRUE, borderWidth = 0, delayForDisplay = 1500) %>%
    highcharter::hc_add_theme(highcharter::hc_theme_google())

hc


```







