---
title: "Incucyte Data Analysis"
output:
  html_document:
    fig.retina: 1
---

# Incucyte Data

This notebook provides infomration about Data derived from the Incucyte automated microscopy device.

## Data structure

Incucyte data must be structured the following way:  

`
Label: HEK_F_1
Metric: PhaseIM Confluence (Percent)
Cell Type: HEK293T_TCF
Passage: 1
Notes: 
Analysis Job: 2017-03-03_HEKTCF_sgRNA_viability1

Date Time	Elapsed	HEK_F_1: HEK293T_TCF (1) 50K / well
03.03.2017 20:00:00	0	5,722833
`

Each well is one column with the SAMPLE separated by the Plate name with a *:*.  
Replicates need to be set!  
If STDErr is also present, this will be always the column next to it!

## Setup parameters

```{r setup}

library(tidyverse)

stderr_present <- FALSE
filepath <- "/Users/janwinter/OneDrive/PhD/Followup/Results/Microscopy/Analysis_Growth_Enrichedpools_TRIAL1-2"
filename <- c("2017-05-17_HEKTCF-HCT116TCF_enrichedpools_TRIAL2_R2.txt")

```

STDErr is present in the file? `r stderr_present`  

File is located in `r filepath` with the name `r filename`.

## Data Handling

```{r load}
if(length(filename) >1 )
{
  for(i in 1:length(filename))
  {
    if(i==1)
    {
      data <- readr:: read_tsv(file = file.path(filepath,filename[i]),col_names = TRUE, skip = 7, locale = readr::locale(decimal_mark = ","))
    } else {
      data <- data %>% dplyr::bind_rows(
        readr:: read_tsv(file = file.path(filepath,filename[i]),col_names = TRUE, skip = 7, locale = readr::locale(decimal_mark = ","))
      )
      
    }
    
  }
} else {
  data <- readr:: read_tsv(file = file.path(filepath,filename),col_names = TRUE, skip = 7, locale = readr::locale(decimal_mark = ","))
}


# get correct colnames
col_names <- colnames(data)
## get all after the ","
#col_names <- sub(pattern = "^.*,\\s+(.*)$", perl = TRUE, replacement = "\\1", x = col_names)
# get rid of file specific things
col_names <- gsub(pattern = "2017-05-12_HEKTCF-HCT116TCF_enrichedpools_TRIAL2_R", perl = TRUE, replacement = "", x = col_names)
col_names <- gsub(pattern = "2017-05-12_HEK-HCTTCF_enrichedTRIAL2", perl = TRUE, replacement = "", x = col_names)
col_names <- gsub(pattern = "[:;,]", perl = TRUE, replacement = "", x = col_names)
col_names <- gsub(pattern = "\\s/", perl = TRUE, replacement = "", x = col_names)
col_names <- gsub(pattern = "^\\s", perl = TRUE, replacement = "", x = col_names)
col_names <- gsub(pattern = "\\(", perl = TRUE, replacement = "", x = col_names)
col_names <- gsub(pattern = "\\)", perl = TRUE, replacement = "", x = col_names)
col_names <- gsub(pattern = "\\s", perl = TRUE, replacement = "_", x = col_names)

colnames(data) <- make.names(col_names, unique = TRUE)
samples <- as.list(col_names[3:length(col_names)])
names(samples) <- col_names[3:length(col_names)]

data.raw <- data
```

## Raw Data

```{r datatable}

filename <- "DATA_exported"
  opts <- list( dom = "Bflrtip",
                lengthMenu = list(c(5, 15, 50, 100, -1), c('5', '15', '50', '100', 'All')), 
                pageLength = 15, scrollX = FALSE)
  opts[["order"]] <- NULL
  opts[["buttons"]] <- list("copy","print", list("extend" = 'csv', "text"='csv', "filename" = filename, "title" = filename), list("extend" = 'excel', "text"='Excel', "filename" = filename, "title" = filename), list("extend" = 'pdf', "text"='pdf', "filename" = filename, "title" = filename))#buttons
  
  ext <- character(0)
  ext <- c(ext, "Buttons")
  ext <- c(ext, "Responsive")

DT::datatable(data, style = "default", class = "display",  options = opts, extensions = ext)

# write table
readr::write_tsv(x = data,path = file.path(filepath,"incucyte_raw.tsv"), append = FALSE)

# # to which data point shall it be normalized?
# # input: get data$elapsed and select one of it
# normselect = 2
# normdata <- dplyr::filter(data,Elapsed == normselect)
# 
# # Normalize Data with the FIRST value for each sample! -> column wise!
# for(i in 3: length(col_names))
# {
#   # divide by the first element of the column
#   data[[i]] <- data[[i]] / normdata[[i]]
# }
# 
# DT::datatable(data,class="stripe hover")

```

# Fitting

Since the individual samples have different starting confluency and subsequent reach the 100% confluence at different time points, we need to
fit the curve to get the slope and curve parameters to compare the viability/cell doubling effects.

```{r growthcurver, eval=FALSE, echo=FALSE}

# days=data$Elapsed
# Vec=data$RLUC
# Gene=data$CFC1
# Vec2=log(Vec)
# Gene2=log(Gene)
# 
# plot(days,Vec2)
# plot(days,Gene2)
# 
# fit_Vec=lm (Vec2 ~ days)
# fit_gene=lm(Gene2 ~ days)
# abline(fit_Vec)
# abline(fit_gene)
# 
# Coef_Vec=fit_Vec$coef
# Coef_gene=fit_gene$coef
# 
# doubling_time_Vec=log(2)/Coef_Vec
# doublint_time_gene=log(2)/Coef_gene
# 
# 

# Idea:
# First, we cut all wells by a specific confluence as a starting point. This is done since lower confluence will result in delayed cell growth as cells require a certain density.
# Second, we cut all samples by a specific confluence end point (95%) to show full confluency
# Third, we re-calculate the hours for each sample starting from this time point
# Fourth, we perform individual well fittings





library(growthcurver)

df_gc <- data.raw
df_gc$`Date Time` <- NULL


# Now, we'll use Growthcurver to summarize the growth curve data using the 
# simple background correction method (minimum value correction). This is the 
# default method, so we don't need to specify it in the command.
# This returns an object of type "gcfit" that holds information about
# the best parameters, the model fit, and additional metrics summarizing
# the growth curve.
gc_fit <- SummarizeGrowth(df_gc$Elapsed, df_gc$`: HEKTCF (1) 50K / well, RLUC`)

# It is easy to get the most useful metrics from a gcfit object, just type:
gc_fit

# And it is easy to plot the raw data and the best fit logistic curve
plot(gc_fit)

# The gcfit object returned from SummarizeGrowth also contains further metrics 
# summarizing the growth curve data.
gc_fit$vals

# look at the structure of the gc_fit object
str(gc_fit)


# To see all the available metrics 
str(gc_fit$vals)


# doubling time is tgen (multiplied by time mearsurement, which is 2 hours)
gc_fit$vals$t_gen * 2


```




```{r sicegar}
library(sicegar)


#View(data)
cols <- colnames(data) # starting AFTER Date Time and Elapsed will be the treatments
# we will always select two columns:
# elapse AND one treatment

# data frame must contain two colums for sicegar, time and intensity
# we will individually go through samples and select those columsn for analysis.



for(i in 3:length(cols))
{
  hours <- "Elapsed"
  colname <- cols[i]
  testdf <- data %>% dplyr::select_(hours, i)

colnames(testdf) <- c("time", "intensity")

    
# Normalize Data
dataOutput = sicegar::normalizeData(testdf, dataInputName = "sample")
dataInput=dataOutput
# Apply dataCheck function to see if data is fine
dataOutputVariable2 = dataCheck(dataInput)

# Do the sigmoidal fit
sigmoidalModel=fitFunction(dataInput=dataInput,
                           model="sigmoidal",
                           n_runs_min=20,
                           n_runs_max=500,
                           showDetails=FALSE)
# 
# (t(sigmoidalModel))


# check if meaningfull
intensityTheoretical=sicegar::sigmoidalFitFormula(testdf$time,
                                                  maximum=sigmoidalModel$maximum_Estimate,
                                                  slope=sigmoidalModel$slope_Estimate,
                                                  midPoint=sigmoidalModel$midPoint_Estimate)
comparisonData=cbind(testdf,intensityTheoretical)


# 
# estimated slop is e.g. 0.07905143
slope <- sigmoidalModel$slope_Estimate
sigmoidalModel$log_likelihood # the higher the better
sigmoidalModel$residual_Sum_of_Squares # the lower the better
# what does it mean?
# we have measurements every two hours, so we can calculate the change in 24 hours by multiplying with 12
# or we just take the slope as it is, which means 
# so for the general calculation we need to assume the following:
# contant time difference between measurement
# input: time difference in hours between measurement
input_timedifference <- 2

# so we calculate the doubling time in hours
growth24h <- slope * (24/input_timedifference) *100 # slope multiplied by number of measurements a day gives the total increase in 24 hours

# alternatively we calculate the number of hours to double the amount of signal according to the slope
# here we divide 100% (1) by the slope to retrieve the number of slope steps to retrieve 100%. since one measurement is 2h  and the slope is calculated using this time difference, we need to correct for it by multiplying with this to get the point were we reach 100%
dbtime <- (1/slope) * input_timedifference
  
if(i==3)
{
  data_list <- list(list("DoublingTime" = dbtime,
                         "24hgrowth" = growth24h,
                         "tidy" = testdf,
                         "fit" = sigmoidalModel,
                         "datainput" = dataInput,
                         "comparisondata" = comparisonData)
                    )
  names(data_list) <- cols[i]
  
  dbtime_tidy <- tibble("Sample" = cols[i],
                        "DoublingTime" = dbtime,
                        "24growth" = growth24h,
                        "Elapsed" = dataInput$timeIntensityData$time,
                        "Value" = dataInput$timeIntensityData$intensity
                        )
  
} else {
  names_old <- names(data_list)
  data_list <- c(data_list, 
                 list(list("DoublingTime" = dbtime,
                         "24hgrowth" = growth24h,
                         "tidy" = data,
                         "fit" = sigmoidalModel,
                         "datainput" = dataInput,
                         "comparisondata" = comparisonData)
                    )
                )
  names(data_list) <- c(names_old, cols[i])
  
  dbtime_tidy_tmp <- tibble("Sample" = cols[i],
                        "DoublingTime" = dbtime,
                        "24growth" = growth24h,
                        "Elapsed" = dataInput$timeIntensityData$time,
                        "Value" = dataInput$timeIntensityData$intensity
                        )
  
  dbtime_tidy <- dbtime_tidy %>% dplyr::bind_rows(dbtime_tidy_tmp)
  
}

}

# write tidy data
readr::write_tsv(x = dbtime_tidy,path = file.path(filepath,"Analysis_tidy.tsv"), append = TRUE,col_names = TRUE)

```

# Plots

## Overall Plot

```{r plot-all-rawdata, results='asis'}

# names can be from names(data_list)
for(i in 1:length(data_list))
{
  
  cat("### ", names(data_list)[i], " \n")
  
  cat("#### ", "Normalized Curve", " \n")
  
  # print fitting data
  g <- ggplot2::ggplot(data_list[[i]]$comparisondata)+
  ggplot2::geom_point(aes(x=time, y=intensity))+
  ggplot2::geom_line(aes(x=time,y=intensityTheoretical))+
  ggplot2::expand_limits(x = 0, y = 0) + 
  ggplot2::theme_bw() + 
  ggplot2::labs(title = names(data_list)[i], sep=" ") 
  
  print(g)
  
  cat("\n ","#### ", "Fitted Curve", " \n")
  
  # Sigmoidal Fit with parameter related lines, ggplot2
g=printInfectionCurves(data_list[[i]]$datainput,
                           sigmoidalFitVector=data_list[[i]]$fit,
                           showParameterRelatedLines=TRUE) +
    ggplot2::theme_bw() + 
    ggplot2::labs(title = names(data_list)[i], sep=" ") 

print(g)
  
}








# print doubling times


cat("## ", "Growth Curves", " \n")

library(highcharter)

hc <- highcharter::highchart() %>%
  highcharter::hc_chart(type="spline",zoomType="xy")%>%
  highcharter::hc_title(text = "Cell Confluence") %>%
  highcharter::hc_subtitle(text = "") %>%
  highcharter::hc_xAxis(title = list(text = "Sample")) %>%
  highcharter::hc_yAxis(title = list(text = "Normalized Confluence in %")) %>%
  highcharter::hc_legend(enabled = TRUE) %>%
  highcharter::hc_exporting(enabled = TRUE,
                 printMaxWidth = 2000,
                 filename = paste(filename, "_Plot_all"),
                 scale=8,
                 formAttributes = list(target = "_blank")
                 )

  for(i in 1:length(unique(names(data_list))))
  {
    sample <- unique(names(data_list))[i]
    plotdata <- dbtime_tidy %>% filter(Sample %in% sample) %>% dplyr::select(Elapsed, Value)
    colnames(plotdata) <- c("x", "y")
    hc <- highcharter::hc_add_series(hc, data = plotdata, name = sample)
  }

  hc <- highcharter::hc_tooltip(hc, crosshairs = TRUE, borderWidth = 0, delayForDisplay = 1500) %>%
    highcharter::hc_add_theme(highcharter::hc_theme_google())

hc


cat("## ", "Doubling Times", " \n")

for(i in 1:length(data_list))
{
  if(i==1)
  {
    dbtimedata <- tibble(
      "Sample" = names(data_list)[i],
      "Time" = data_list[[i]]$DoublingTime
    ) 
  } else
    {
       dbtimedata <- dbtimedata %>% dplyr::bind_rows( tibble(
      "Sample" = names(data_list)[i],
      "Time" = data_list[[i]]$DoublingTime) )
    }
  
}

# remove empty
dbtimedata <- dbtimedata %>% dplyr::filter(Sample != "Empty")
# make plot

ggplot(data=dbtimedata, aes(x=Sample, y=Time))+
  geom_boxplot() +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
  labs(title = paste("Calculated Doubling Time" ), x = "Samples", y = "Doubling Time [h]") +
    ggplot2::theme_bw() +
    ggplot2::geom_hline(yintercept = 0) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = rel(1.1)), legend.position="none")



```

```{r plot-all, eval=FALSE}
library(highcharter)

hc <- highcharter::highchart() %>%
  highcharter::hc_chart(type="spline",zoomType="xy")%>%
  highcharter::hc_title(text = "Cell Confluence") %>%
  highcharter::hc_subtitle(text = "for all sampled with median replicates") %>%
  highcharter::hc_xAxis(title = list(text = "Sample")) %>%
  highcharter::hc_yAxis(title = list(text = paste("Normalized Confluence in Foldchange to", normselect, "hours from start", sep= " ") )) %>%
  highcharter::hc_legend(enabled = TRUE) %>%
  highcharter::hc_exporting(enabled = TRUE,
                 printMaxWidth = 2000,
                 filename = paste(filename, "_Plot_all"),
                 scale=8,
                 formAttributes = list(target = "_blank")
                 )

  for(i in 1:length(samples))
  {
    plotdata <- data[,c("Elapsed",names(samples)[i])]
    colnames(plotdata) <- c("x", "y")
    hc <- highcharter::hc_add_series(hc, data = plotdata, name = names(samples)[i])
  }

  hc <- highcharter::hc_tooltip(hc, crosshairs = TRUE, borderWidth = 0, delayForDisplay = 1500) %>%
    highcharter::hc_add_theme(highcharter::hc_theme_google())

hc


```

## All Data as ggplot

```{r ggplot-all, eval=FALSE, echo=FALSE}


```


```{r ggplot-normalize, eval=FALSE, echo=FALSE}


```



# Calculate rates of change




