---
title: "qPCR Lentivirus Integration"
author: "Jan Winter"
date: "17 Mai 2016"
output: 
  html_document: 
    keep_md: yes
---


# Estimation of Lentivirus Copy Number Integration (CNI) after Infection

This will estimate the number of successfull integrations of WPRE after infection with a lentivirus containing a WPRE site.

## Settings

- Infected cells: 100000
- Vector used: MarieU6-onchip

```{r loadfile, eval=TRUE, warning=FALSE,message=FALSE, echo=FALSE, dpi=300}

library(DT)
library(knitr)

path <- "/Users/janwinter/Documents/PhD/Results/qPCR/2016-08-08_MOI_Lib4_Lib5_Lib6_Lib7"
knitr::opts_chunk$set(root.dir = path)
# JAN Lib4-5_check
excel.sheet <- file.path(path,"qPCR_VirusTiter_Template.xlsx")
setwd(path)





# Jan TRIAL4 new standards
#excel.sheet <- "/Users/janwinter/Documents/PhD/Results/qPCR/2016-06-27_qPCR_MOI_Screens_new-Standards/qPCR_VirusTiter_Template.xlsx"
#setwd("/Users/janwinter/Documents/PhD/Results/qPCR/2016-06-27_qPCR_MOI_Screens_new-Standards")

MOI.desired <- 0.4

# Output from qPCR Machine
#rawdata <- read.table(file = "/Users/janwinter/Desktop/test.txt", header = TRUE, sep="\t", fill = TRUE)
# Each Sample is a own data frame with the following columns:
#   Well | Condition | Cq Value
# Later we will add columns:
# CN (Copy number) | CNI (Copy number integration)

# ALL DATA IS READ BY WELL defined! e.g. A1, A5 or B7

# Load qPCR Worksheet
## contains:
### - Overview
### - Reagents
### - SampleDefinition
### - Calibration
### - qPCRData
### - cDNA
### - Mastermix
library(openxlsx)
overview <- as.matrix(openxlsx::read.xlsx(xlsxFile = excel.sheet, sheet = "Overview"))
cDNA <-as.data.frame(openxlsx::read.xlsx(xlsxFile = excel.sheet, sheet = "cDNA"))
mastermix <-as.data.frame(openxlsx::read.xlsx(xlsxFile = excel.sheet, sheet = "mastermix"))
standards <- as.data.frame(openxlsx::read.xlsx(xlsxFile = excel.sheet, sheet = "Calibration"))
#samples <- openxlsx::read.xlsx(xlsxFile = excel.sheet, sheet = "SampleDefinition")
qPCRData <- openxlsx::read.xlsx(xlsxFile = excel.sheet, sheet = "qPCRData")
qPCRData <- merge.data.frame(x=qPCRData, y=cDNA[,c("Type","q_PCR_Well_Pos","Sample")], by.x= "Pos", by.y = "q_PCR_Well_Pos", all.x=TRUE)

# Remove bad calibration points
#standards <- standards[-c(1,7),] # the two highest ones..


# Print tables

DT::datatable(qPCRData, class="hover", caption = "qPCR Rawdata")

DT::datatable(standards, class="hover", caption = "Standards used for Linear Regression")

```

## Plate Setup

```{r plateview-setup, eval=TRUE, warning=FALSE,message=FALSE, echo=FALSE, dpi=300}
knitr::opts_chunk$set(root.dir = path)

#httr::with_config(httr::use_proxy(url = "http://www-int2.inet.dkfz-heidelberg.de", port=80, auth="basic"), devtools::install_github("briandconnelly/ggplot2bdc"))

platemap <- as.data.frame(cDNA)
# Add qPCR data value if present


library(dplyr)
 
platemap <- dplyr::mutate(platemap,
                   Row=as.numeric(match(toupper(substr(q_PCR_Well_Pos, 1, 1)), LETTERS)),
                   Column=as.numeric(substr(q_PCR_Well_Pos, 2, 5)))

platemapmastermix <- as.data.frame(mastermix)
platemapmastermix <- dplyr::mutate(platemapmastermix,
                   Row=as.numeric(match(toupper(substr(q_PCR_Well_Pos, 1, 1)), LETTERS)),
                   Column=as.numeric(substr(q_PCR_Well_Pos, 2, 5)))


library(ggplot2)
 


ggplot(data=platemap, aes(x=Column, y=Row)) +
    geom_point(data=expand.grid(seq(1, 24), seq(1, 16)), aes(x=Var1, y=Var2),
               color="grey90", fill="white", shape=21, size=6) +
    geom_point(size=10) +
    coord_fixed(ratio=(13/12)/(9/8), xlim=c(0.5, 24.5), ylim=c(0.5, 16.5)) +
    scale_y_reverse(breaks=seq(1, 16), labels=LETTERS[1:16]) +
    scale_x_continuous(breaks=seq(1, 24)) +
    labs(title="Occupied Wells")

# 
# library(ggplot2bdc)
 
# ggplot(data=platemap, aes(x=Column, y=Row)) +
#     geom_point(data=expand.grid(seq(1, 24), seq(1, 16)), aes(x=Var1, y=Var2),
#                color="grey90", fill="white", shape=21, size=6) +
#     geom_point(size=10) +
#     coord_fixed(ratio=(13/12)/(9/8), xlim=c(0.5, 24.5), ylim=c(0.5, 16.5)) +
#     scale_y_reverse(breaks=seq(1, 8), labels=LETTERS[1:8]) +
#     scale_x_continuous(breaks=seq(1, 24)) +
#     labs(title="Plate Layout for My Experiment") 
#     #theme_bdc_microtiter() # only for 96-wells..

# Plate all Samples

platemap$Type <- as.factor(platemap$Type)
 
ggplot(data=platemap, aes(x=Column, y=Row)) +
    geom_point(data=expand.grid(seq(1, 24), seq(1, 16)), aes(x=Var1, y=Var2),
               color="grey90", fill="white", shape=21, size=6) +
    geom_point(aes(shape=Type, colour=Sample), size=6) +
    coord_fixed(ratio=(13/12)/(9/8), xlim=c(0.5, 24.5), ylim=c(0.5, 16.5)) +
    scale_y_reverse(breaks=seq(1, 16), labels=LETTERS[1:16]) +
    scale_x_continuous(breaks=seq(1, 24)) +
  scale_shape_manual(values=seq(from=0, to = length(unique(platemap$Type)), by=1 ) ) +
    labs(title="Plate Layout: Sample Types") #+
    #theme_bdc_microtiter()

# Plate as TEXT
ggplot(data=platemap, aes(x=Column, y=Row, label=platemap$Sample)) +
  
    geom_text(aes(colour=Sample), size=2) + 
  
    #geom_point(data=expand.grid(seq(1, 24), seq(1, 16)), aes(x=Var1, y=Var2),
    #           color="grey90", fill="white", shape=21, size=6) +
    #geom_point(aes(shape=Type, colour=Sample), size=6) +
    coord_fixed(ratio=(13/12)/(9/8), xlim=c(0.5, 24.5), ylim=c(0.5, 16.5)) +
    scale_y_reverse(breaks=seq(1, 16), labels=LETTERS[1:16]) +
    scale_x_continuous(breaks=seq(1, 24)) +
  scale_shape_manual(values=seq(from=0, to = length(unique(platemap$Type)), by=1 ) ) +
    labs(title="Plate Layout: Added Virus [uL]") #+
    #theme_bdc_microtiter()

# Plate as Genes

ggplot(data=platemapmastermix, aes(x=Column, y=Row)) +
    geom_point(data=expand.grid(seq(1, 24), seq(1, 16)), aes(x=Var1, y=Var2),
               color="grey90", fill="white", shape=21, size=6) +
    geom_point(aes(colour=Sample), size=6) +
    coord_fixed(ratio=(13/12)/(9/8), xlim=c(0.5, 24.5), ylim=c(0.5, 16.5)) +
    scale_y_reverse(breaks=seq(1, 16), labels=LETTERS[1:16]) +
    scale_x_continuous(breaks=seq(1, 24)) +
    labs(title="Plate Mastermix Layout for My Experiment") #+

########## 96 Well master plates

cDNAplate <- as.data.frame(cDNA)
cDNAplate <- mutate(platemap,
                   Row=as.numeric(match(toupper(substr(Rack.Position, 1, 1)), LETTERS)),
                   Column=as.numeric(substr(Rack.Position, 2, 5)))

mastermixplate <- as.data.frame(mastermix)
mastermixplate <- mutate(mastermixplate,
                   Row=as.numeric(match(toupper(substr(Rack.Position, 1, 1)), LETTERS)),
                   Column=as.numeric(substr(Rack.Position, 2, 5)))

# PLate 96 Well plates for qPCR preparation

# cDNA plate
ggplot(data=cDNAplate, aes(x=Column, y=Row)) +
    geom_point(data=expand.grid(seq(1, 12), seq(1, 8)), aes(x=Var1, y=Var2),
               color="grey90", fill="white", shape=21, size=6) +
    geom_point(aes(shape=Type, colour=Sample), size=6) +
    coord_fixed(ratio=(13/12)/(9/8), xlim=c(0.5, 12.5), ylim=c(0.5, 8.5)) +
    scale_y_reverse(breaks=seq(1, 8), labels=LETTERS[1:8]) +
    scale_x_continuous(breaks=seq(1, 12)) +
  scale_shape_manual(values=seq(from=0, to = length(unique(cDNAplate$Type)), by=1 ) ) +
    labs(title="cDNA Master Plate") #+
    #theme_bdc_microtiter()

# Mastermix plate
ggplot(data=mastermixplate, aes(x=Column, y=Row)) +
    geom_point(data=expand.grid(seq(1, 12), seq(1, 8)), aes(x=Var1, y=Var2),
               color="grey90", fill="white", shape=21, size=6) +
    geom_point(aes( colour=Sample), size=6) +
    coord_fixed(ratio=(13/12)/(9/8), xlim=c(0.5, 12.5), ylim=c(0.5, 8.5)) +
    scale_y_reverse(breaks=seq(1, 8), labels=LETTERS[1:8]) +
    scale_x_continuous(breaks=seq(1, 12)) +
    labs(title="qPCR Mastermix Plate") #+
    #theme_bdc_microtiter()






```


# qPCR Data

```{r plate-cq, eval=TRUE, warning=FALSE,message=FALSE, echo=FALSE, dpi=300}
knitr::opts_chunk$set(root.dir = path)

####### Plot qPCR rawdata

qPCRplate <- as.data.frame(qPCRData)
qPCRplate <- mutate(qPCRplate,
                   Row=as.numeric(match(toupper(substr(Pos, 1, 1)), LETTERS)),
                   Column=as.numeric(substr(Pos, 2, 5)))

qPCRplate$Cp <- round(as.numeric(qPCRplate$Cp), digits=2)

ggplot(data=qPCRplate, aes(x=Column, y=Row, label=qPCRplate$Cp)) +
  
    geom_text(size=1.5) + 
  
    #geom_point(data=expand.grid(seq(1, 24), seq(1, 16)), aes(x=Var1, y=Var2),
    #           color="grey90", fill="white", shape=21, size=6) +
    #geom_point(aes(shape=Type, colour=Sample), size=6) +
    coord_fixed(ratio=(13/12)/(9/8), xlim=c(0.5, 24.5), ylim=c(0.5, 16.5)) +
    scale_y_reverse(breaks=seq(1, 16), labels=LETTERS[1:16]) +
    scale_x_continuous(breaks=seq(1, 24)) +
  #scale_shape_manual(values=seq(from=0, to = length(unique(qPCRplate$Type)), by=1 ) ) +
    labs(title="qPCR RAW Cq Values") #+



# Plate text and colors

qPCRplate$Type <- as.factor(qPCRplate$Type)
qPCRplate$Cp <- as.character(qPCRplate$Cp)
qPCRplate$Cp[is.na(qPCRplate$Cp)] <- "-"
 
ggplot(data=qPCRplate, aes(x=Column, y=Row, label=qPCRplate$Cp)) +
    geom_text(aes(colour=Sample), size=1.5) +
   # geom_point(data=expand.grid(seq(1, 24), seq(1, 16)), aes(x=Var1, y=Var2),
    #           color="grey90", fill="white", shape=21, size=6) +
    #geom_point(aes(colour=Sample), size=6) +
    coord_fixed(ratio=(13/12)/(9/8), xlim=c(0.5, 24.5), ylim=c(0.5, 16.5)) +
    scale_y_reverse(breaks=seq(1, 16), labels=LETTERS[1:16]) +
    scale_x_continuous(breaks=seq(1, 24)) +
  #scale_shape_manual(values=seq(from=0, to = length(unique(qPCRplate$Type)), by=1 ) ) +
    labs(title="qPCR RAW Cq values") #+


```

## Standards and qPCR Calculations

```{r calculations, eval=TRUE, warning=FALSE,message=FALSE, echo=FALSE, dpi=300}
knitr::opts_chunk$set(root.dir = path)

############################################
############ STANNDARDS ####################
############################################

### Get Standards and the Values
# Names of Standards
standards.names <- unique(standards$Gene)

# Get Data and construct list
list.standard <- list()
list.model <- list()

for(i in 1:length(standards.names))
{
  df <- as.data.frame(standards[standards$Gene == standards.names[[i]],])
  # Add data from qPCR
  df$Data <- sapply(df$Wells, function(x){
    # Get well data
    wells <- unlist(strsplit(as.character(x),","))
    #print(str(wells))
    return(mean(as.numeric(qPCRData[qPCRData$Pos %in% wells,"Cp"]), na.rm=TRUE) )
  })
  
  # make log of concentration
  df$Sample <- log10(df$Sample)
  if(i==1)
  {
    list.standard <- list(df)
    list.model <- list(NA)
  }
  else
  {
    list.standard <- c(list.standard, list(df))
    list.model <- c(list.model, list(NA))
  }
}
# Set Names
names(list.standard) <- standards.names
names(list.model) <- standards.names

# Fit linear regression

for ( i in 1:length(list.model))
{
  # model <- (lm(Sample ~ Data, data=list.standard[[i]]))
  model <- lm(Data ~ Sample, data=list.standard[[i]])
  cat("\n")
  cat("\n")
  print(names(list.standard)[i])
  print(summary(model))
  
  # Save list
  list.model[[i]] <- model
  
  # make plots
  cat("\n")
  plot(y = list.standard[[i]]$Data, x=list.standard[[i]]$Sample, xlab = "Log10 Molecules", ylab = "Cq Value", main = paste("Standard", names(list.standard)[i], sep=" "))
  abline(model, lwd=2, col="red")
}

############################################
########### Load qPCR data #################
############################################


# Predict qPCR Values on linear regression model (LOG10 fitted!)

  # Get data for each sample for this gene
  

# get samples
predicted.data <- data.frame(
  Well = cDNA$q_PCR_Well_Pos,
  Sample = cDNA$Sample,
  Type = cDNA$Type,
  Replicate = cDNA$Replicate,
  stringsAsFactors = FALSE
)

# Add Gene information from mastermix plate
predicted.data$Gene <- sapply(predicted.data$Well, function(x){
  
  return(mastermix[mastermix$q_PCR_Well_Pos == x,"Sample"])
})

# Add raw Cq values (0.0034 ng per haploid genome)
predicted.data$Cq <- NA

# Add new volumns
predicted.data$Fit <- ""
predicted.data$CN <- ""
#predicted.data$lwr <- ""
#predicted.data$upr <- ""


for(i in 1:nrow(predicted.data))
{
  
  # get cq value and predicted copy number from standard curve
  cq <- as.numeric(qPCRData[qPCRData$Pos == predicted.data[i,"Well"] ,"Cp"])
  # Since we use Y~X and we want to know which Y leads to which X, we cannot use the linear regression model for calculations directly,
  # thus we need to make the formula from y= to x=
  
  cc <- coef(list.model[[predicted.data[i,"Gene"]]])
  xnew <- (cq-cc[1])/cc[2]
  
  #predicted <- predict(object = list.model[[predicted.data[i,"Gene"]]], data.frame(Data = cq),  level = 0.9, interval = "confidence")
  
  predicted.data[i,"Cq"] <- as.numeric(cq)
  predicted.data[i,"Fit"] <- as.numeric(xnew)
  #predicted.data[i,"Fit"] <- as.numeric(predicted[1])
  #predicted.data[i,"lwr"] <- as.numeric(predicted[2])
  #predicted.data[i,"upr"] <- as.numeric(predicted[3])
  predicted.data[i,"CN"] <- as.numeric(10^(xnew))
  
  
}










#     
# predicted.data <- do.call(rbind.data.frame, apply(samples,1,function(x){
#     # get Cq value from qPCRData
#     wells <- unlist(strsplit(x["Wells"],","))
#     
#     for(u in 1:length(wells))
#     {
#       
#       cq <- as.numeric(qPCRData[qPCRData$Pos == wells[u] ,"Cp"])
#       predicted <- predict(object = list.model[[x["Gene"]]], data.frame(Data = cq),  level = 0.9, interval = "confidence")
#       if(u == 1)
#       {
#         
#         return.well <- data.frame( "Wells" = wells[[u]], 
#                                    "Fit" = as.numeric(predicted[1]),
#                                    "lwr" = as.numeric(predicted[2]),
#                                    "upr" = as.numeric(predicted[3]),
#                                    "Gene" = x["Gene"],
#                                    "Type" = x["Type"],
#                                    "Sample" = x["Sample"],
#                                    stringsAsFactors = FALSE)
#       }
#       else
#       {
#         return.well <- rbind.data.frame(return.well,
#                                         c(wells[[u]], 
#                                     as.numeric(predicted[1]),
#                                     as.numeric(predicted[2]),
#                                     as.numeric(predicted[3]),
#                                    x["Gene"],
#                                     x["Type"],
#                                    x["Sample"]) )
#       }
#       if(u == length(wells))
#       {
#         return(return.well)  
#       }
#       
#     }
# 
#   }) )
#   

#colnames(predicted.data) <- c("Well","Fit","lwr","upr","Gene","Type","Sample")
rownames(predicted.data) <- predicted.data[,"Well"]

# Convert back from log10
#predicted.data <- as.data.frame(t(predicted.data), stringsAsFactors = FALSE)
predicted.data$Fit <- as.numeric(10^(as.numeric(predicted.data$Fit)))
#predicted.data$lwr <- as.numeric(10^(as.numeric(predicted.data$lwr)))
#predicted.data$upr <- as.numeric(10^(as.numeric(predicted.data$upr)))

to.compare <- c("WPRE","GAPDH")
list.predicted <- list("WPRE" = NA, "GAPDH" = NA)
for(i in 1:length(to.compare))
{
  
  list.predicted[[i]] <- predicted.data[predicted.data$Gene == to.compare[i],]
  
}

##########
########## Already calculated: copy number accoridng to standards
#### Now: we calculate the copy number per cell by dividing the number of WPRE copies by the number of GAPDH, and multiple the result by 2 since two GAPDH copies are present in hek cells.

predicted.data$MOIfit <- NA

for(i in 1:nrow(predicted.data))
{
 
  if(predicted.data[i,"Gene"] == "WPRE")
  {
    
    # Now we check the sample, type and replicate and use the combination, to find the matching replicate with the gene GAPDH, which is the reference gene!
    wpre <- as.numeric(predicted.data[i,"Fit"])
    gapdh <- as.numeric(predicted.data[predicted.data$Sample == predicted.data[i,"Sample"] & predicted.data$Type == predicted.data[i,"Type"] & predicted.data$Replicate == predicted.data[i,"Replicate"] & predicted.data[,"Gene"] ==  "GAPDH","Fit"])
    
    #print(wpre)
    #print(gapdh)
     if(is.na(wpre) || is.na(gapdh) )
    {
      predicted.data[i,"MOIfit"] <- NA
    }
    else
    {
      predicted.data[i,"MOIfit"] <- as.numeric(wpre / gapdh )*2
    }
    
  }
 
}

# predicted.data$MOIlwr <- NA
# 
# for(i in 1:nrow(predicted.data))
# {
#   
#   if(predicted.data[i,"Gene"] == "WPRE" && predicted.data[i,"Type"] !="MIX")
#   {
#     
#     # Now we check the sample, type and replicate and use the combination, to find the matching replicate with the gene GAPDH, which is the reference gene!
#     wpre <- as.numeric(predicted.data[i,"lwr"])
#     gapdh <- as.numeric(predicted.data[predicted.data$Sample == predicted.data[i,"Sample"] & predicted.data$Type == predicted.data[i,"Type"] & predicted.data$Replicate == predicted.data[i,"Replicate"] & predicted.data[,"Gene"] ==  "GAPDH","lwr"])
#     
#     # print(wpre)
#     # print(gapdh)
#     if(is.na(wpre) || is.na(gapdh) )
#     {
#       predicted.data[i,"MOIlwr"] <- NA
#     }
#     else
#     {
#       predicted.data[i,"MOIlwr"] <- as.numeric(wpre / gapdh )*2
#     }
#     
#   }
# }
# 
# 
# predicted.data$MOIupr <- NA
# 
# for(i in 1:nrow(predicted.data))
# {
#   
#   if(predicted.data[i,"Gene"] == "WPRE" && predicted.data[i,"Type"] !="MIX")
#   {
#     
#     # Now we check the sample, type and replicate and use the combination, to find the matching replicate with the gene GAPDH, which is the reference gene!
#     wpre <- as.numeric(predicted.data[i,"upr"])
#     gapdh <- as.numeric(predicted.data[predicted.data$Sample == predicted.data[i,"Sample"] & predicted.data$Type == predicted.data[i,"Type"] & predicted.data$Replicate == predicted.data[i,"Replicate"] & predicted.data[,"Gene"] ==  "GAPDH","upr"])
#     
#     # print(wpre)
#     # print(gapdh)
#     if(is.na(wpre) || is.na(gapdh) )
#     {
#       predicted.data[i,"MOIupr"] <- NA
#     }
#     else
#     {
#       predicted.data[i,"MOIupr"] <- as.numeric(wpre / gapdh )*2
#     }
#     
#     
#   }
# }



### Print table

DT::datatable(predicted.data, class="hover", caption = "qPCR Data Calculations")

```

## Plateplot Results

```{r plateplotresults, eval=TRUE, warning=FALSE,message=FALSE, echo=FALSE, dpi=300}
knitr::opts_chunk$set(root.dir = path)
#### MAKE PLATEPLOTS WITH RESULTS

resultmap <- mutate(predicted.data,
                   Row=as.numeric(match(toupper(substr(Well, 1, 1)), LETTERS)),
                   Column=as.numeric(substr(Well, 2, 5)))

### plot FIT

resultmap$Type <- as.factor(resultmap$Type)
resultmap$Sample <- as.factor(resultmap$Sample)
resultmap$CN <- as.character(round(as.numeric(resultmap$CN), digits = 2))
resultmap$MOIfit <- as.character(round(as.numeric(resultmap$MOIfit), digits = 2))
resultmap$C1[is.na(resultmap$Cq)] <- "-"
 
ggplot(data=resultmap, aes(x=Column, y=Row, label=resultmap$CN)) +
    geom_text(aes(colour=Sample), size=1.5) +
   # geom_point(data=expand.grid(seq(1, 24), seq(1, 16)), aes(x=Var1, y=Var2),
    #           color="grey90", fill="white", shape=21, size=6) +
    #geom_point(aes(colour=Sample), size=6) +
    coord_fixed(ratio=(13/12)/(9/8), xlim=c(0.5, 24.5), ylim=c(0.5, 16.5)) +
    scale_y_reverse(breaks=seq(1, 16), labels=LETTERS[1:16]) +
    scale_x_continuous(breaks=seq(1, 24)) +
  #scale_shape_manual(values=seq(from=0, to = length(unique(qPCRplate$Type)), by=1 ) ) +
    labs(title="Copy Numbers per Well according to Linear Regression of the Standard") #+



 
ggplot(data=resultmap, aes(x=Column, y=Row, label=resultmap$MOIfit)) +
    geom_text(aes(colour=Type), size=1.5) +
   # geom_point(data=expand.grid(seq(1, 24), seq(1, 16)), aes(x=Var1, y=Var2),
    #           color="grey90", fill="white", shape=21, size=6) +
    #geom_point(aes(colour=Sample), size=6) +
    coord_fixed(ratio=(13/12)/(9/8), xlim=c(0.5, 24.5), ylim=c(0.5, 16.5)) +
    scale_y_reverse(breaks=seq(1, 16), labels=LETTERS[1:16]) +
    scale_x_continuous(breaks=seq(1, 24)) +
  #scale_shape_manual(values=seq(from=0, to = length(unique(qPCRplate$Type)), by=1 ) ) +
    labs(title="Calculated Mean Copy Number per Cell according to Linear Regression") #+



```

## Highcharter MOI Plots

```{r highcharts, eval=TRUE, warning=FALSE,message=FALSE, echo=FALSE, dpi=300}
knitr::opts_chunk$set(root.dir = path)
###########
########## CREATE HIGHCHARTER PLOTS



# Make data rdy for plot, mean replicates
list.samples <- as.list(unique(predicted.data$Type))
names(list.samples) <- unique(predicted.data$Type)

plot.output <- as.list(unique(predicted.data$Type))
names(plot.output) <- unique(predicted.data$Type)


for(i in 1:(length(list.samples)))
{
  
  # Make final DF
  # df.WPRE <- data.frame(
  # "Type" = unique(predicted.data[predicted.data$Gene=="WPRE" & predicted.data$Sample==names(list.samples)[i],"Type"]),
  # #"Sample" = unique(predicted.data[predicted.data$Gene=="WPRE","Sample"]),
  # stringsAsFactors = FALSE
  # )
  
  
  ######## CREATE HIGHCHARTER PLOT
  
  # Add MEAN per replicate + SD
    
  df.WPRE <- aggregate.data.frame(predicted.data[predicted.data$Gene=="WPRE" & predicted.data$Type==names(list.samples)[i],c("MOIfit")], by = list(predicted.data[predicted.data$Gene=="WPRE" & predicted.data$Type==names(list.samples)[i],"Sample"]), FUN = function(x) { mean(x, na.rm=TRUE) })
  colnames(df.WPRE) <- c("Sample","MOIfit")
  
  df.WPRE$Sample <- as.numeric(df.WPRE$Sample)
  

  
  colnames(df.WPRE) <- c("Concentration", "Predicted MOI")
  
  # Sort
  list.samples[[i]] <- df.WPRE[order(df.WPRE$Concentration),]
  
  # Rdy for output
  
  library(highcharter)
  
  hc <- highcharter::highchart()
  hc <- highcharter::hc_chart(hc, type = "line", zoomType="xy")
  hc <- highcharter::hc_title(hc, text = paste("MOI for", names(list.samples)[i], sep=" "))
  hc <- highcharter::hc_subtitle(hc, text = "Calculated MOI by CopyNumber detection using GAPDH")
  hc <- highcharter::hc_xAxis(hc, title = list(text = "Added Virus [uL]"),
                                       categories = as.character( list.samples[[i]]$Concentration)  )
  hc <- highcharter::hc_yAxis(hc,
        title = list(text = "Calculated MEAN MOI"),
        align = "left",
        showFirstLabel = FALSE,
        showLastLabel = FALSE,
        labels = list(useHTML = TRUE)
      )
    
  # Add Fitted MOI Data
  hc <- highcharter::hc_add_series(hc, name = "MOI Fitted", data =  list.samples[[i]][,"Predicted MOI"])
  
  # Add MOI 0.4 Line
  hc <- highcharter::hc_add_series(hc, name = "MOI of 0.4", data = rep(x=MOI.desired, times = nrow(list.samples[[i]])))


  hc <- highcharter::hc_legend(hc, enabled = TRUE)
  hc <- highcharter::hc_exporting(hc, enabled = TRUE)
  hc <- highcharter::hc_tooltip(hc, crosshairs = TRUE,
             shared = TRUE, borderWidth = 0)

  hc <- highcharter::hc_add_theme(hc, highcharter::hc_theme_google())

  plot.output[[i]] <- hc

}



##### Higcharter plot combined ALL IN ONE


library(highcharter)
  
  hc <- highcharter::highchart()
  hc <- highcharter::hc_chart(hc, zoomType="xy")
  hc <- highcharter::hc_title(hc, text = paste("MOI for", names(list.samples)[i], sep=" "))
  hc <- highcharter::hc_subtitle(hc, text = "Calculated MOI by CopyNumber detection using GAPDH")
  #hc <- highcharter::hc_xAxis(hc, title = list(text = "Applied Sample Concentration"),
   #                                    categories = seq(from=1, to = length(unique(predicted.data$Sample)), by=1) )  
  hc <- highcharter::hc_yAxis(hc,
        title = list(text = "Calculated MEAN MOI"),
        align = "left",
        showFirstLabel = FALSE,
        showLastLabel = FALSE,
        labels = list(useHTML = TRUE)
      )
    
  # Add Fitted MOI Data
  for(i in 1:(length(list.samples)-2) )
  {
    
    df <- list.samples[[i]]
    if(class(df) == "data.frame")
    {
      print(df)
      colnames(df) <- c("x","y")
      hc <- highcharter::hc_add_series_df(hc, type = "scatter", data =  df, name = as.character(names(list.samples)[i]))  
    }

  }
  
 
  # Add MOI 0.4 Line
  hc <- highcharter::hc_add_series(hc, type="scatter", name = "MOI of 0.4", data = rep(x=MOI.desired, times = nrow(list.samples[[i]])))


  hc <- highcharter::hc_legend(hc, enabled = TRUE)
  hc <- highcharter::hc_exporting(hc, enabled = TRUE)
  hc <- highcharter::hc_tooltip(hc, crosshairs = TRUE,
             shared = TRUE, borderWidth = 0)

  #hc <- highcharter::hc_add_theme(hc, highcharter::hc_theme_google())

  hc

## from predicted data
  
hchart(predicted.data, type="scatter", x = Sample, y = MOIfit, group=Type, class=Sample) %>% hc_chart(zoomType="xy")


# Write to Excel
# wb <- openxlsx::loadWorkbook(excel.sheet , xlsxFile = NULL)
# for(i in 1:length(list.samples))
# {
#   
#   openxlsx::addWorksheet(wb, paste("Analysis", names(list.samples)[i], sep="_") )
#   openxlsx::writeDataTable(wb, paste("Analysis", names(list.samples)[i], sep="_"), x = list.samples[[i]], startCol = 1, startRow = 1, xy = NULL,
# colNames = TRUE, rowNames = FALSE, tableStyle = "TableStyleLight9",
# tableName = names(list.samples)[i], headerStyle = NULL, withFilter = TRUE,
# keepNA = FALSE)
#   
#   
# }
# 
# # Save Workbook
# openxlsx::saveWorkbook(wb, file = excel.sheet, overwrite = TRUE)






```

## CopyNumber Calculation

Copy Numbers have been calculated by:

- calculation of the CopyNumber of both WPRE and GAPDH by linear regression on log10 transformed Molecules (Standard Curve)
- CopyNumber of WPRE was then divided by the CopyNumber of the respective GAPDH value
- Since GAPDH is present twice, we multiple the result by 2

Desired MOI: `r MOI.desired`

Finally we receive the number of WPRE integrations in a diploid genome of the pool of cells infected with a certain amount of virus

```{r CN, echo=FALSE, eval=TRUE, results="asis"}
knitr::opts_chunk$set(root.dir = path)



# 
# ggplot(data=qPCRplate, aes(x=Column, y=Row, label=qPCRplate$Cp)) +
#     geom_text(aes(colour=Sample), size=2.5) +
#    # geom_point(data=expand.grid(seq(1, 24), seq(1, 16)), aes(x=Var1, y=Var2),
#     #           color="grey90", fill="white", shape=21, size=6) +
#     #geom_point(aes(colour=Sample), size=6) +
#     coord_fixed(ratio=(13/12)/(9/8), xlim=c(0.5, 24.5), ylim=c(0.5, 16.5)) +
#     scale_y_reverse(breaks=seq(1, 16), labels=LETTERS[1:16]) +
#     scale_x_continuous(breaks=seq(1, 24)) +
#   #scale_shape_manual(values=seq(from=0, to = length(unique(qPCRplate$Type)), by=1 ) ) +
#     labs(title="Plate Layout for My Experiment") #+









plot.output[[1]]
plot.output[[2]]
plot.output[[3]]
plot.output[[4]]
plot.output[[5]]
plot.output[[6]]
plot.output[[7]]
plot.output[[8]]
plot.output[[9]]
plot.output[[10]]
plot.output[[11]]
plot.output[[12]]
plot.output[[13]]
plot.output[[14]]
plot.output[[15]]
plot.output[[16]]
plot.output[[17]]
plot.output[[18]]
plot.output[[19]]
plot.output[[20]]
plot.output[[21]]
plot.output[[22]]
plot.output[[23]]
plot.output[[24]]
plot.output[[25]]
plot.output[[26]]



# for(i in 1:length(list.samples))
# {
#   cat("\n")
#   cat("### ", "Copy Number Calculation for Library: ", names(list.samples)[i])
#   cat("\n")
#   
#   cat("\n")
#   cat(paste(names(list.samples)[i]))
#   cat("\n")
#   print(knitr::kable(list.samples[[i]]))
#   cat("\n")
# }

```


