---
title: "TidyDF_Visualization"
author: "Jan Winter"
date: "24 April 2017"
output:
  html_document:
    fig_width: 10
    fig.retina: 1
  pdf_document: default
---

# Load all CSV files into a single, large tidy tibble

```{r setup, include=FALSE}
library(tidyverse)
# load CSV files
path <- "/Users/janwinter/OneDrive/PhD/Followup/Results/Luciferase/CSV/HCT116/"
file <- "HCT116TCF_all"

files <- list.files(path = path ,pattern="*.csv")

for(i in 1:length(files))
{
  # do bind_rows to add those, they all have the same column structure
 if(i == 1){
   # initialise
   
   data_tibble <- readr::read_csv(file = file.path(path, files[i]),col_names = TRUE,progress = TRUE)
   data_tibble$File <- files[i]
 } else {
   
   #data_tibble <- readr::read_csv(file = file.path(path, files[i]),col_names = TRUE,progress = TRUE) %>% dplyr::bind_rows(data_tibble)
   data_tibble2 <- readr::read_csv(file = file.path(path, files[i]),col_names = TRUE,progress = TRUE)
   data_tibble2$File <- files[i]
   data_tibble <- data_tibble %>% dplyr::bind_rows(data_tibble2)
 } 
  
}

# remove X1
data_tibble$X1 <- NULL


```

Data loaded from `r path` stored in `r length(files)` CSV files.  

# All Data

```{r all-data}

library(DT)

DT::datatable(data_tibble)

```


# Make plots

First we replace numbers to only get back gene symbols.  
Then we select the genes we want to investigate and plot them without and with 50ng/mL Wnt stimulation.  


```{r makeplots}
# remove any _3 etc from gene names

data_tibble$Treatment <- sub(pattern = "_\\d{1,2}", replacement = "",x = data_tibble$Treatment)
data_tibble$Treatment <- sub(pattern = "_p\\d{1,2}", replacement = "",x = data_tibble$Treatment)
data_tibble$Treatment <- sub(pattern = "^TOP$", replacement = "Topflash",x = data_tibble$Treatment)
data_tibble$Treatment <- sub(pattern = "^TOP_", replacement = "Topflash_",x = data_tibble$Treatment)

data_tibble$Treatment <- sub(pattern = "^SPRY_", replacement = "SPRY2_",x = data_tibble$Treatment)
data_tibble$Treatment <- sub(pattern = "^B1GALT1", replacement = "B4GALT1",x = data_tibble$Treatment)
data_tibble$Treatment <- sub(pattern = "^NPBWr", replacement = "NPBWR",x = data_tibble$Treatment)
data_tibble$Treatment <- sub(pattern = "^Kremen1", replacement = "KREMEN1",x = data_tibble$Treatment)


data_tibble$Treatment <- sub(pattern = "TOPFLASH", replacement = "Topflash",x = data_tibble$Treatment)
data_tibble$Treatment <- sub(pattern = "Wnt3", replacement = "Wnt",x = data_tibble$Treatment)

```


# Remove LOW values

Then we remove all measurements with LOW RLUC levels as we expect something went wrong for thos

```{r removelowrluc}
RLUCthresh <- 50

# Eliminate all entries with LOW RLUC values
data_tibble <- data_tibble %>% dplyr::filter(RLUC.mean > RLUCthresh)


# check for plates where px459 calibrated to itself is > 1.2 (should not be possible, plate may be bad)
Fileremove <- data_tibble %>% filter(Treatment == "px459", Divided > 1.5) %>% dplyr::select(File) %>% .$File
data_tibble <- data_tibble %>% filter(!File %in% Fileremove)

Fileremove <- data_tibble %>% filter(Treatment == "px459_Wnt", Divided > 1.5, Divided < 0.6) %>% dplyr::select(File) %>% .$File
data_tibble <- data_tibble %>% filter(!File %in% Fileremove)


```

# Safe tidy data in CSV

```{r savetidy}

write_tsv(x = data_tibble, path = paste(file,".tsv", sep=""),append = FALSE,col_names = TRUE)
```

# make Wnt treatment separate and plot a ranked boxplot

```{r heatmap}
data_heat <- data_tibble

# make additional column with Wnt 1 or 0
data_heat <- data_heat %>% dplyr::mutate(Wnt = grepl(pattern = ".*Wnt.*",x = Treatment))


# Try 1: Wnt vs no Wnt
# make two columns: Log2 without and Log2 with Wnt treatment
#df <-  tibble( "Gene" = unique(sub(pattern="_Wnt", x = data_heat$Treatment, replacement = "") ))


Wnt <- data_heat %>% dplyr::filter(Wnt == TRUE) %>% dplyr::select(Treatment,Log2)
noWnt <- data_heat %>% dplyr::filter( Wnt == FALSE) %>% dplyr::select(Treatment,Log2)


ggplot(data=Wnt, aes(x=reorder(Treatment, Log2), y=Log2))+
  geom_boxplot() +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
  labs(title = "Calibrated Ratio Wnt stimulated", x = "Samples", y = "Calibrated Ratio to CTRL") +
    ggplot2::theme_bw() +
    ggplot2::geom_hline(yintercept = 0) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = rel(1.1)), legend.position="none")


ggplot(data=noWnt, aes(x=reorder(Treatment, Log2), y=Log2))+
  geom_boxplot() +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
  labs(title = "Calibrated Ratio", x = "Samples", y = "Calibrated Ratio to CTRL") +
    ggplot2::theme_minimal() +
    ggplot2::geom_hline(yintercept = 0) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = rel(1.1)), legend.position="none")

# 
# data2<- data_heat %>% dplyr::select(Log2)
# data3 <- as.matrix(data2)
# data2_t <- t(data2)
# #colnames(data2_t) <- data_heat$Treatment
# # remove Wnt in names
# colnames(data2_t) <- sub(pattern="_Wnt", x = data_heat$Treatment, replacement = "") 
# anno_col <- data.frame(row.names = seq.int(from=1, to= length(colnames(data2_t))), "Wnt" = as.numeric(data_heat$Wnt)  )
# anno_col[anno_col$Wnt == 1, "Wnt"] = "on"
# anno_col[anno_col$Wnt == 0, "Wnt"] = "off"
# 
# rownames(data2_t) <- c("Log2")
# gp = gpar(fill = "green")
# pheatmap::pheatmap(data2_t, 
#                    cluster_row = F,
#                    cluster_cols = T,
#                    annotation_col = anno_col,
#                   
#                   
#                    fontsize = 6.5,
#                    fontsize_row=6, 
#                    fontsize_col = 6,
#                    gaps_col=50)


```


## Without WNT stimulation

```{r no-wnt, dpi=300}
# select genes
genes <- c("APC","Topflash","CFC1","B4GALT6", "B4GALT7", "FARP2", "KLHL22", "KIF21A","KRT36","RASAL3", "RIC1", "CEP55","LIMS1","FRMD5","DNAJB14","B4GALT1", "PAQR7","TMEM191B", "px459")

data <- dplyr::filter(data_tibble, Treatment %in% genes)

 p <- ggplot(data, aes(x=Treatment, y=Divided, fill=Treatment)) + 
    geom_boxplot() +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
    labs(title = "Calibrated Ratio", x = "Samples", y = "Calibrated Ratio to CTRL") +
    ggplot2::theme_minimal() +
    ggplot2::geom_hline(yintercept = 1) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = rel(1.1)), legend.position="none")
  
 p
 
 
 
  p <- ggplot(data, aes(x=Treatment, y=RLUC, fill=Treatment)) + 
    geom_boxplot() +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
    labs(title = "Calibrated RLUC", x = "Samples", y = "Calibrated RLUC to CTRL") +
    ggplot2::theme_minimal() +
    ggplot2::geom_hline(yintercept = 1) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = rel(1.1)), legend.position="none")
  
 p
 
 
 data <- dplyr::filter(data_tibble, Treatment %in% genes)
 
 p <- ggplot(data, aes(x=Treatment, y=Log2, fill=Treatment)) + 
    geom_boxplot() +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
    labs(title = "Log2 Calibrated Ratio", x = "Samples", y = "Log2 Calibrated Ratio to CTRL") +
    ggplot2::theme_minimal() +
    ggplot2::geom_hline(yintercept = 0) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = rel(1.1)), legend.position="none")
  
 p
```


## With Wnt Stimulation

```{r wnt, dpi=300}
# select genes
genes_wnt <- c("APC_Wnt","Topflash_Wnt","CFC1_Wnt","B4GALT6_Wnt", "B4GALT7_Wnt", "FARP2_Wnt", "KLHL22_Wnt", "KIF21A_Wnt","KRT36_Wnt","RASAL3_Wnt", "RIC1_Wnt", "CEP55_Wnt","LIMS1_Wnt","FRMD5_Wnt","DNAJB14_Wnt","B4GALT1_Wnt", "PAQR7_Wnt","TMEM191B_Wnt", "px459_Wnt")

data <- dplyr::filter(data_tibble, Treatment %in% genes_wnt)

 p <- ggplot(data, aes(x=Treatment, y=Divided, fill=Treatment)) + 
    geom_boxplot() +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
    labs(title = "Calibrated Ratio with Wnt Stimulation", x = "Samples", y = "Calibrated Ratio to CTRL") +
    ggplot2::theme_minimal() +
    ggplot2::geom_hline(yintercept = 1) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = rel(1.1)), legend.position="none")
  
 p
 
 # Log 2
 
  p <- ggplot(data, aes(x=Treatment, y=Log2, fill=Treatment)) + 
    geom_boxplot() +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
    labs(title = "Calibrated Ratio with Wnt Stimulation", x = "Samples", y = "Log2 Calibrated Ratio to CTRL") +
    ggplot2::theme_minimal() +
    ggplot2::geom_hline(yintercept = 0) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = rel(1.1)), legend.position="none")
  
 p
 
 
 
```




