---
title: "TidyDF_Visualization_qPCR"
author: "Jan Winter"
date: "22 Mai 2017"
output:
  html_document:
    fig_width: 10
    fig.retina: 1
  pdf_document: default
---

# Load all CSV files into a single, large tidy tibble

```{r setup, include=FALSE}
library(tidyverse)
# load CSV files
path <- "/Users/janwinter/OneDrive/PhD/Followup/Results/qPCR/2017-06-26_candidate_expression/"


files <- list.files(path = path ,pattern="*.csv")

for(i in 1:length(files))
{
  # do bind_rows to add those, they all have the same column structure
 if(i == 1){
   # initialise
   
   data_tibble <- readr::read_csv(file = file.path(path, files[i]),col_names = TRUE,progress = TRUE)
   data_tibble$File <- files[i]
 } else {
   
   #data_tibble <- readr::read_csv(file = file.path(path, files[i]),col_names = TRUE,progress = TRUE) %>% dplyr::bind_rows(data_tibble)
   data_tibble2 <- readr::read_csv(file = file.path(path, files[i]),col_names = TRUE,progress = TRUE)
   data_tibble2$File <- files[i]
   data_tibble <- data_tibble %>% dplyr::bind_rows(data_tibble2)
 } 
  
}

# remove X1
data_tibble$X1 <- NULL


```

Data loaded from `r path` stored in `r length(files)` CSV files.  

# All Data

```{r all-data}

library(DT)

DT::datatable(data_tibble)

```


# Safe tidy data in TSV

```{r savetidy}

write_tsv(x = data_tibble, path = file.path(path, paste("All_Tidy",".tsv", sep="") ),append = FALSE,col_names = TRUE)
```

# Select Data

We always make sure selecting the ones that have seen the same calibrator -> calibrator column  
Moreover we need to make sure the filename contains HCT for HCT data or not HCT for not HCT data.  


```{r plot}

# select data with calibrator
data <- data_tibble %>% filter(Calibrator == "RLUC") %>% filter(!grepl("HCT", File)) %>% filter(!grepl("qPCR_data_calibrated_tidy.csv", File))

# log2 transform data FC
data$FC <- log2(data$FC)

# Samples available
unique(data$Sample)

data <- data %>% filter(Sample %in% c("APC","CK1A","FARP2","KLHL22","DNAJB14","KIF21A","KRT36","PAQR7"))

# first we plot:
# BCAT, APC, CK1A, CFC1, KIF21A, FARP2, KRT36, DNAJB14, TMEM191B, KLHL22, PAQR7, B4GALT6 and B4GAlt7 (all!)

# Heatmap

library(gplots)

x  <- as.matrix(data[c("FC","Sample","Gene")])

data(mtcars)
x  <- as.matrix(mtcars)
rc <- rainbow(nrow(x), start=0, end=.3)
cc <- rainbow(ncol(x), start=0, end=.3)

heatmap.2(x)

library(pheatmap)
pheatmap::pheatmap(t(data[c("FC","Sample")]), 
                   cluster_row = T,
                   cluster_cols = F,
                   #annotation_col = annotation_col,
                   #annotation_row = annotation_row,
                   color = col.pal, 
                   fontsize = 6.5,
                   fontsize_row=6, 
                   fontsize_col = 6,
                   gaps_col=50)

# if we want we can restrict it to certain genes!
data <- data %>% dplyr::filter(Gene %in% c("GAPDH","PGK1","IPO8","PPIA"))


# plot all samples against all selected genes
ggplot(data=data, aes(x=reorder(Gene, FC), y=FC))+
  geom_boxplot() +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
  labs(title = "Relative, calibrated mRNA Expression", x = "Target Genes", y = "Log2 Relative Expression Calibrated to RLUC") +
    ggplot2::theme_bw() +
    ggplot2::geom_hline(yintercept = 0) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = rel(1.1)), legend.position="none")

ggsave(filename = "qPCR_plot1.png",device = "png",dpi = 300,width = 10)

# Plot data grouped by sample!

ggplot(data=data, aes(x=reorder(Gene, FC), y=FC))+
  geom_bar(aes(fill = Sample),stat = "identity", position = "dodge") +
    #geom_jitter(shape=16, position=position_jitter(0.2)) +
  labs(title = "Relative, calibrated mRNA Expression", x = "Target Genes", y = "Log2 Relative Expression Calibrated to RLUC") +
    ggplot2::theme_bw() +
    ggplot2::geom_hline(yintercept = 0) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = rel(1.1)), legend.position="bottom")

ggsave(filename = "qPCR_plot2.png",device = "png",dpi = 300,width = 10)


ggplot(data=data, aes(x=Gene, y=FC))+
  geom_bar(aes(fill = Sample),stat = "identity", position = "dodge") +
    #geom_jitter(shape=16, position=position_jitter(0.2)) +
  labs(title = "Relative, calibrated mRNA Expression", x = "Target Genes", y = "Log2 Relative Expression Calibrated to RLUC") +
    ggplot2::theme_bw() +
    ggplot2::geom_hline(yintercept = 0) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = rel(1.1)), legend.position="bottom")

ggsave(filename = "qPCR_plot3.png",device = "png",dpi = 300,width = 10)



# only gene in which APC/CK1A show difference

data <- data %>% dplyr::filter(Gene %in% c("ADAM10","AXIN2","DKK1","MYC","NOTCH2","EDN","ARMCX1","BIRC5","DKK4"))

ggplot(data=data, aes(x=Gene, y=FC))+
  geom_bar(aes(fill = Sample),stat = "identity", position = "dodge") +
    #geom_jitter(shape=16, position=position_jitter(0.2)) +
  labs(title = "Relative, calibrated mRNA Expression", x = "Target Genes", y = "Log2 Relative Expression Calibrated to RLUC") +
    ggplot2::theme_bw() +
    ggplot2::geom_hline(yintercept = 0) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = rel(1.1)), legend.position="bottom")

ggsave(filename = "qPCR_HEK.png",device = "png",dpi = 300,width = 10)


ggplot(data=data, aes(x=reorder(Gene, FC), y=FC))+
  geom_bar(aes(fill = Sample),stat = "identity", position = "dodge") +
    #geom_jitter(shape=16, position=position_jitter(0.2)) +
  labs(title = "Relative, calibrated mRNA Expression", x = "Target Genes", y = "Log2 Relative Expression Calibrated to RLUC") +
    ggplot2::theme_bw() +
    ggplot2::geom_hline(yintercept = 0) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = rel(1.1)), legend.position="bottom")

ggsave(filename = "qPCR_HEK_ordered.png",device = "png",dpi = 300,width = 10)


# 
# data2<- data_heat %>% dplyr::select(Log2)
# data3 <- as.matrix(data2)
# data2_t <- t(data2)
# #colnames(data2_t) <- data_heat$Treatment
# # remove Wnt in names
# colnames(data2_t) <- sub(pattern="_Wnt", x = data_heat$Treatment, replacement = "") 
# anno_col <- data.frame(row.names = seq.int(from=1, to= length(colnames(data2_t))), "Wnt" = as.numeric(data_heat$Wnt)  )
# anno_col[anno_col$Wnt == 1, "Wnt"] = "on"
# anno_col[anno_col$Wnt == 0, "Wnt"] = "off"
# 
# rownames(data2_t) <- c("Log2")
# gp = gpar(fill = "green")
# pheatmap::pheatmap(data2_t, 
#                    cluster_row = F,
#                    cluster_cols = T,
#                    annotation_col = anno_col,
#                   
#                   
#                    fontsize = 6.5,
#                    fontsize_row=6, 
#                    fontsize_col = 6,
#                    gaps_col=50)


```


## Without WNT stimulation

```{r no-wnt, dpi=300}
# select genes
genes <- c("APC","Topflash","CFC1","B4GALT6", "B4GALT7", "FARP2", "KLHL22", "KIF21A","KRT36","RASAL3", "RIC1", "CEP55","LIMS1","FRMD5","DNAJB14","B4GALT1", "PAQR7","TMEM191B", "px459")

data <- dplyr::filter(data_tibble, Treatment %in% genes)

 p <- ggplot(data, aes(x=Treatment, y=Divided, fill=Treatment)) + 
    geom_boxplot() +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
    labs(title = "Calibrated Ratio", x = "Samples", y = "Calibrated Ratio to CTRL") +
    ggplot2::theme_minimal() +
    ggplot2::geom_hline(yintercept = 1) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = rel(1.1)), legend.position="none")
  
 p
 
 
 
  p <- ggplot(data, aes(x=Treatment, y=RLUC, fill=Treatment)) + 
    geom_boxplot() +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
    labs(title = "Calibrated RLUC", x = "Samples", y = "Calibrated RLUC to CTRL") +
    ggplot2::theme_minimal() +
    ggplot2::geom_hline(yintercept = 1) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = rel(1.1)), legend.position="none")
  
 p
 
 
 data <- dplyr::filter(data_tibble, Treatment %in% genes)
 
 p <- ggplot(data, aes(x=Treatment, y=Log2, fill=Treatment)) + 
    geom_boxplot() +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
    labs(title = "Log2 Calibrated Ratio", x = "Samples", y = "Log2 Calibrated Ratio to CTRL") +
    ggplot2::theme_minimal() +
    ggplot2::geom_hline(yintercept = 0) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = rel(1.1)), legend.position="none")
  
 p
```


## With Wnt Stimulation

```{r wnt, dpi=300}
# select genes
genes_wnt <- c("APC_Wnt","Topflash_Wnt","CFC1_Wnt","B4GALT6_Wnt", "B4GALT7_Wnt", "FARP2_Wnt", "KLHL22_Wnt", "KIF21A_Wnt","KRT36_Wnt","RASAL3_Wnt", "RIC1_Wnt", "CEP55_Wnt","LIMS1_Wnt","FRMD5_Wnt","DNAJB14_Wnt","B4GALT1_Wnt", "PAQR7_Wnt","TMEM191B_Wnt", "px459_Wnt")

data <- dplyr::filter(data_tibble, Treatment %in% genes_wnt)

 p <- ggplot(data, aes(x=Treatment, y=Divided, fill=Treatment)) + 
    geom_boxplot() +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
    labs(title = "Calibrated Ratio with Wnt Stimulation", x = "Samples", y = "Calibrated Ratio to CTRL") +
    ggplot2::theme_minimal() +
    ggplot2::geom_hline(yintercept = 1) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = rel(1.1)), legend.position="none")
  
 p
 
 # Log 2
 
  p <- ggplot(data, aes(x=Treatment, y=Log2, fill=Treatment)) + 
    geom_boxplot() +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
    labs(title = "Calibrated Ratio with Wnt Stimulation", x = "Samples", y = "Log2 Calibrated Ratio to CTRL") +
    ggplot2::theme_minimal() +
    ggplot2::geom_hline(yintercept = 0) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = rel(1.1)), legend.position="none")
  
 p
 
 
 
```




